Psychological Needs During Intergroup Contact

### 2022-01-04 Methods-and-Results.Rmd
table adjustments

```{r descrOutWide, include=FALSE}
# Outgroup Interaction Sample Descriptives Table --- wider version
rbind(
  workerOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Descr Out Wide",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWide.tex")

>>>>

```{r descrOutWide, include=FALSE}
# Outgroup Interaction Sample Descriptives Table --- wider version
rbind(
  workerOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Descr Out Wide",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWide.tex")

### 2022-01-04 Tables/studentOutVarDescr.tex
re-run with descriptives test
table adjustments

\caption{Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.44** & 0.49*** & -0.22 & 0.51*** & 0.14\\
Competence & 0.23*** &  & 0.58*** & 0.40** & 0.55*** & 0.21\\
Autonomy & 0.12*** & 0.24*** &  & 0.22 & 0.61*** & 0.05\\
Relatedness & 0.48*** & 0.31*** & 0.38*** &  & 0.35* & -0.09\\
Quality & 0.19*** & 0.40*** & 0.16*** & 0.15*** &  & 0.16\\
Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.23*** & 0.30*** & \\
\addlinespace
Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 78.80 & 70.41\\
Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.44** & 0.49*** & -0.22 & 0.51*** & 0.14\\
Competence & 0.23*** &  & 0.58*** & 0.40** & 0.55*** & 0.21\\
Autonomy & 0.12*** & 0.24*** &  & 0.22 & 0.61*** & 0.05\\
Relatedness & 0.48*** & 0.31*** & 0.38*** &  & 0.35* & -0.09\\
Quality & 0.19*** & 0.40*** & 0.16*** & 0.15*** &  & 0.16\\
Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.23*** & 0.30*** & \\
\addlinespace
Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 78.80 & 70.41\\
Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
Within SD & NA & NA & NA & NA & NA & NA\\
ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
Within.person.SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2022-01-04 Tables/studentVarDescr.tex
z test
methods and results re-run
initial descriptive table merge
re-run with descriptives test
table adjustments

\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.60*** & 0.66*** & 0.43*** & 0.78*** & 0.11\\
Competence & 0.24*** &  & 0.71*** & 0.65*** & 0.74*** & 0.09\\
Autonomy & 0.15*** & 0.34*** &  & 0.56*** & 0.67*** & -0.06\\
Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.54*** & -0.11\\
Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.10\\
Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.10*** & 0.12*** & \\
\addlinespace
Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.60*** & 0.66*** & 0.43*** & 0.78*** & 0.11\\
Competence & 0.24*** &  & 0.71*** & 0.65*** & 0.74*** & 0.09\\
Autonomy & 0.15*** & 0.34*** &  & 0.56*** & 0.67*** & -0.06\\
Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.54*** & -0.11\\
Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.10\\
Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.10*** & 0.12*** & \\
\addlinespace
Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
Within SD & NA & NA & NA & NA & NA & NA\\
ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
Within.person.SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2022-01-04 Tables/workerOutVarDescr.tex
re-run with descriptives test
table adjustments

\caption{Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.82*** & 0.60*** & 0.32 & 0.52** & -0.03\\
Competence & 0.36*** &  & 0.89*** & 0.24 & 0.38 & -0.24\\
Autonomy & 0.28*** & 0.23*** &  & 0.29 & 0.56** & 0.02\\
Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.14\\
Quality & 0.17*** & 0.44*** & 0.27*** & 0.27*** &  & 0.50*\\
Attitudes NL & 0.24*** & 0.37*** & 0.24*** & 0.37*** & 0.52*** & \\
\addlinespace
Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.82*** & 0.60*** & 0.32 & 0.52** & -0.03\\
Competence & 0.36*** &  & 0.89*** & 0.24 & 0.38 & -0.24\\
Autonomy & 0.28*** & 0.23*** &  & 0.29 & 0.56** & 0.02\\
Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.14\\
Quality & 0.17*** & 0.44*** & 0.27*** & 0.27*** &  & 0.50*\\
Attitudes NL & 0.24*** & 0.37*** & 0.24*** & 0.37*** & 0.52*** & \\
\addlinespace
Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
Within SD & NA & NA & NA & NA & NA & NA\\
ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
Within.person.SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2022-01-04 Tables/workerVarDescr.tex
AOT-M contact H results rendered
z test
run but not rendered
re-run with descriptives test
table adjustments

\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
\addlinespace
Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
\addlinespace
Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
Within SD & NA & NA & NA & NA & NA & NA\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
Within.person.SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}
